---
title: "Fraud's prediction model"
author: "Daniel Tedeschi Samaia"
date: "09/12/2020"
output:
  html_document:
    df_print: paged
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
header-includes: \usepackage{hyperref}
always_allow_html: yes
---
\newpage


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


__Import necessary libraries__ 
```{r  message=FALSE, eval = FALSE}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(FSelector)  
library(e1071)
library(caTools)
library(vctrs)
library(ROSE)
library(caret)
library(randomForest)
library(pROC) 
library(partykit)
library(CustomerScoringMetrics)
library(plyr)
library(tree)
library(MASS)
```


__Read the CSV files__
```{r  message=FALSE, eval = FALSE}

#data to be used in models later
datasmall <- read_csv("datafile_small.csv")

data <- read_csv("datafile_full.csv")

#We tested models that are more time consuming on a smaller dataset
```

\newpage

# Data Preparation

```{r  message=FALSE, eval = FALSE}

#convert target into factor
data$target <- as.factor(data$target)

#Check levels of the target variable
levels(data$target)

#remove id
data$ID_code <- NULL

#remove na
data <- na.omit(data)

#Repeat the same with small dataset
datasmall$target <- as.factor(datasmall$target)

#Check levels of the target variable
levels(datasmall$target)

#remove id
datasmall$ID_code <- NULL

#remove na
datasmall <- na.omit(datasmall)
```


## Apply Stratified Sampling
```{r  message=FALSE, eval = FALSE}
#Use stratified sampling for large dataset
set.seed(10)
stratified_data <- splitstackshape::stratified(data, "target", 0.7)
```



## Splitting
```{r  message=FALSE, eval = FALSE}

set.seed(123)

# Split large stratified dataset into training and test sets
split= caTools:: sample.split(stratified_data$target, SplitRatio =0.70)

training_set = subset(stratified_data, split==TRUE)
test_set =subset(stratified_data, split==FALSE)

#Split small dataset into training and test sets
split2= caTools:: sample.split(datasmall$target, SplitRatio =0.70)

training_set_small = subset(datasmall, split2==TRUE)
test_set_small =subset(datasmall, split2==FALSE)
```

\newpage

# Code for Top 3 best performing models

## Random Forest

### Undersampling
```{r  message=FALSE, eval = FALSE}
#Apply undersampling to the large dataset to be used with Random Forest
set.seed(123)
undersample_data <- ROSE:: ovun.sample(target~. , data = training_set, method = "under",
                                                                 p = 0.5, seed = 1)$data
```

### Selecting top 100 attributes based on their Information Gain
```{r  message=FALSE, eval = FALSE}

attribute_weights_under <- FSelector::information.gain(target~., undersample_data)
attribute_weights_under <- attribute_weights_under %>% arrange(desc(attr_importance))
selected_attribute_under <- FSelector:: cutoff.k(attribute_weights_under, 100)

undersampledata <- undersample_data[selected_attribute_under]
undersampledata$target=undersample_data$target
```

### Model
```{r  message=FALSE, eval = FALSE}
#Random Forest tuning
training_features_under <- subset(undersampledata, select = -target)

set.seed(111)
tuneRF(training_features_under, undersampledata$target, mtryStart = 3, ntree = 500,
       stepFactor = 1.5, improve = 0.01)

RF_model_under<- randomForest(target~., undersampledata, mtry = 3, ntree = 500)

prediction_RF_under<- predict(RF_model_under, test_set)

(cf_random_under_70_100IG <- caret:: confusionMatrix(prediction_RF_under, 
                 test_set$target, positive = '1', mode = "prec_recall"))
```

### Check RF for overfitting
```{r  message=FALSE, eval = FALSE}
prediction_RF_under_train <- predict(RF_model_under, training_set)

(cf_random_under_70_100IG_train <- caret:: confusionMatrix(prediction_RF_under_train,
                         training_set$target, positive = '1', mode = "prec_recall"))
```

## SVM

### Oversampling
```{r  message=FALSE, eval = FALSE}
set.seed(123)

oversample_data_70 <- ROSE:: ovun.sample(target~. , data = training_set_small,
                                      method = "over", p = 0.5, seed = 1)$data
```

### Selecting all attributes with positive Information Gain
```{r  message=FALSE, eval = FALSE}

attribute_weights_over_70_pos <- FSelector:: information.gain(target~., oversample_data_70)

selected_attribute_over_70_pos <- attribute_weights_over_70_pos
%>% filter(attr_importance > 0) %>% 
mutate(indexNames = row.names.data.frame(.)) %>% pull(., indexNames)

oversample_data_all_70_pos <- oversample_data_70
oversample_data_70_pos <- oversample_data_all_70_pos[selected_attribute_over_70_pos]
oversample_data_70_pos$target <- oversample_data_all_70_pos$target
```

### Model
```{r  message=FALSE, eval = FALSE}
svm_model_over_linear_70_pos <- e1071:: svm(target~., data = oversample_data_70_pos,
                                    kernel="linear", scale=TRUE, probability = TRUE)


svm_prediction_over_linear_70_pos <- predict(svm_model_over_linear_70_pos, test_set_small)

(cf_svm_over_linear_70_pos <- caret:: confusionMatrix(svm_prediction_over_linear_70_pos,
                          test_set_small$target, positive = "1", mode = "prec_recall"))
```

### Check SVM for overfitting
```{r  message=FALSE, eval = FALSE}
svm_prediction_over_linear_70_pos_fitting <- predict(svm_model_over_linear_70_pos,          
                                                           oversample_data_70_pos)

(cf_svm_over_linear_70_pos_fitting <- caret::
confusionMatrix(svm_prediction_over_linear_70_pos_fitting,
oversample_data_70_pos$target, positive = "1", mode = "prec_recall"))
```

## LDA

### Oversampling
```{r  message=FALSE, eval = FALSE}

set.seed(123)
ov_training <- ovun.sample(target~., data = training_set_small, method = "over",
                                                        p = .5, seed = 10)$data
```

### Model
```{r  message=FALSE, eval = FALSE}

lda_ov <- lda(target~., ov_training)
predict_lda <- predict(lda_ov, test_set_small, type="class")$class
(cf_lda_over_70=confusionMatrix(predict_lda, test_set_small$target,
                                positive="1",mode="prec_recall"))
```

### Check LDA for overfitting
```{r  message=FALSE, eval = FALSE}
predict_lda_overfitting <- predict(lda_ov, ov_training, type="class")$class
(cf_lda_over_70_fitting=confusionMatrix(predict_lda_overfitting, ov_training$target,
                                                  positive="1",mode="prec_recall"))
```

\newpage

# Plots for top 3 models

## ROC plots
```{r  message=FALSE, eval = FALSE}

RF_model_under_prob=predict(RF_model_under, test_set, type ="prob")[,2]
SVMpred <- predict(svm_model_over_linear_70_pos , test_set_small, probability = TRUE)
SVM_prob <- attr(SVMpred, "probabilities")[,2]
LDA_prob <- predict(lda_ov, test_set_small, type="prob")$posterior[,2]
```

```{r  message=FALSE, eval = FALSE}

roc_RF=roc(test_set$target, RF_model_under_prob)
roc_SVM <- roc(test_set_small$target, SVM_prob)
roc_LDA <- roc(test_set_small$target, LDA_prob)


df_RF = data.frame((1-roc_RF$specificities), roc_RF$sensitivities)
df_SVM = data.frame((1-roc_SVM$specificities), roc_SVM$sensitivities)
df_LDA = data.frame((1-roc_LDA$specificities), roc_LDA$sensitivities)
```

```{r  message=FALSE, eval = FALSE}

plot(df_RF, col="red", type="l",     
xlab="False Positive Rate (1-Specificity)",
ylab="True Positive Rate (Sensitivity)", main="ROC Chart")
lines(df_SVM, col="blue")             
lines(df_LDA, col="green") 
grid(NULL, lwd = 1)

abline(a = 0, b = 1, col = "lightgray")

legend("bottomright",
c("Random Forest","SVM", "LDA"),
fill=c("red","blue", "green"))
```

## AUC Table
```{r  message=FALSE, eval = FALSE}

auctable=tibble("model"=c("RF", "SVM", "LDA"),"AUC"=c(auc(roc_RF), 
                                     auc(roc_SVM), auc(roc_LDA)))
auctable
```

## Cumulative Gain Charts
```{r  message=FALSE, eval = FALSE}

GainTable_RF <- cumGainsTable(RF_model_under_prob, test_set$target, resolution = 1/100)
GainTable_SVM <- cumGainsTable(SVM_prob, test_set_small$target, resolution = 1/100)
GainTable_LDA <- cumGainsTable(LDA_prob, test_set_small$target, resolution = 1/100)
```

```{r  message=FALSE, eval = FALSE}

plot(GainTable_RF[,4], col="red", type="l", lwd = 2,   
xlab="Percentage of test instances", 
ylab="Percentage of correct predictions", main="Cumulative Gain Chart")
lines(GainTable_SVM[,4], col="blue", type ="l",lwd = 2)
lines(GainTable_LDA[,4], col="green", type ="l",lwd = 2)
grid(NULL, lwd = 1)

legend("bottomright",
c("Random Forest","SVM", "LDA"),
fill=c("red","blue","green"))

abline(a = 0, b = 1, col = "lightgray")
```

## Lift Charts
```{r  message=FALSE, eval = FALSE}

liftChart(predict_lda , test_set_small$target)
liftChart(svm_prediction_over_linear_70_pos , test_set_small$target)
liftChart(prediction_RF_under, test_set$target)
```

\newpage

#Other model types used in report

## GLM

### Oversampling
```{r  message=FALSE, eval = FALSE}

data.over <- ovun.sample(target~., data=training_set_small, method="over", seed=10)$data
```

### GLM Model 1
```{r  message=FALSE, eval = FALSE}

log_reg <- glm(target ~.,data.over, family = "binomial")
log_reg_predict <- predict(log_reg, test_set_small, type = "response")
log_reg_class <- ifelse(log_reg_predict >0.6, "1", "0")
log_reg_class <- as.factor(log_reg_class)
cf_glm_over_70 <- confusionMatrix(log_reg_class, test_set_small$target, positive = "1",
                                                                  mode = "prec_recall")
```

### Undersampling 
```{r  message=FALSE, eval = FALSE}
data.under <- ovun.sample(target~., data=training_set_small, method="under", seed=10)$data
```

### GLM Model 2
```{r  message=FALSE, eval = FALSE}

log_reg2U <- glm(target ~.,data.under, family = "binomial")
log_reg_predict2U <- predict(log_reg2U, test_set_small, type = "response")
log_reg_class2U <- ifelse(log_reg_predict2U >0.65, "1", "0")
log_reg_class2U <- as.factor(log_reg_class2U)
cf_glm_under_70 <- confusionMatrix(log_reg_class2U, test_set_small$target, positive = "1",
                                                                     mode = "prec_recall")
```

## Decision trees

### Oversampling
```{r  message=FALSE, eval = FALSE}
oversample_data_70 <- ROSE:: ovun.sample(target~. , data = training_set_small,
                                     method = "over", p = 0.5, seed = 1)$data
```

### Selecting top 100 attributes based on their Information Gain
```{r  message=FALSE, eval = FALSE}

attrweights_over_70 <- FSelector:: information.gain(target~., oversample_data_70)
attrweights_over_70 <- attrweights_over_70 %>% arrange(desc(attr_importance))
selectedattr_over_70 <- FSelector:: cutoff.k(attrweights_over_70, 100)


oversample_70 <- oversample_data_70[selectedattr_over_70]
oversample_70$target <- oversample_data_70$target
```

### Tree() Model
```{r  message=FALSE, eval = FALSE}

regtree_70_over <- tree(target~., data=oversample_70)
summary(regtree_70_over)
print(regtree_70_over)

plot(regtree_70_over)
text(regtree_70_over)

regtree_70_over_pre <- predict(regtree_70_over, test_set_small, type="class")
correct_regtree_70_over <- which(test_set_small$target == regtree_70_over_pre)
length(correct_regtree_70_over)

cf_tree_over_70_100IG <- confusionMatrix(regtree_70_over_pre,
test_set_small$target, positive='1', mode = "prec_recall")
```

### Ctree() Model
```{r  message=FALSE, eval = FALSE}

DeTree_70_over <- ctree(target~., data=oversample_70)

DeTree_70_over_pre <- predict(DeTree_70_over, test_set_small)
correct_DeTree_70_over <- which(test_set_small$target == DeTree_70_over_pre)
length(correct_DeTree_70_over)
(accuracy_DeTree_70_over <- length(correct_DeTree_70_over)/nrow(test_set_small)*100)

cf_ctree_70_100IG <- confusionMatrix(DeTree_70_over_pre, 
test_set_small$target, positive='1', mode = "prec_recall")
```

## Other SVMs used

### Splitting using 60/40 ratio
```{r  message=FALSE, eval = FALSE}

split_60 <- caTools:: sample.split(datasmall$target, SplitRatio =0.6)

training_set_60 <- subset(datasmall, split_60 ==TRUE)
test_set_60 <-subset(datasmall, split_60 ==FALSE)
```

### Both sampling
```{r  message=FALSE, eval = FALSE}

set.seed(123)

bothsample_data_60 <- ROSE:: ovun.sample(target~. , data = training_set_60,
                                   method = "both", p = 0.5, seed = 1)$data
```

### Selecting all attributes with positive Information Gain
```{r  message=FALSE, eval = FALSE}

attribute_weights_both_60_pos <- FSelector:: information.gain(target~., bothsample_data_60)
selected_attribute_both_60_pos <- attribute_weights_both_60_pos %>%
filter(attr_importance > 0) %>% mutate(indexNames = row.names.data.frame(.)) %>%
                                                              pull(.,indexNames)


bothsample_data_all_60_pos <- bothsample_data_60
bothsample_data_60_pos <- bothsample_data_all_60_pos[selected_attribute_both_60_pos]
bothsample_data_60_pos$target <- bothsample_data_all_60_pos$target
```

### SVM Model 1
```{r  message=FALSE, eval = FALSE}

svm_model_both_radial_60_pos <- e1071:: svm(target~., data = bothsample_data_60_pos,                     kernel="radial", scale=TRUE, probability = TRUE)
svm_prediction_both_radial_60_pos <- predict(svm_model_both_radial_60_pos, test_set_60)

(cf_svm_both_radial_60_pos <- caret:: confusionMatrix(svm_prediction_both_radial_60_pos,
                              test_set_60$target, positive = "1", mode = "prec_recall"))
```

### Additional SVM Model with tuning 
```{r  message=FALSE, eval = FALSE}
svm_for_tuning_no_sampling_60 <-e1071:: svm(target~., data = training_set_60,
                                                           kernel = "radial")

tune_out_60 = e1071:: tune(method = "svm",  target~. , data = training_set_60,
             kernel = "radial", tunecontrol = e1071::tune.control(cross = 10))

svm_prediction_tune_60 <- predict(tune_out_60$best.model, test_set_60)
cf_svm_prediction_tune_60 <- caret:: confusionMatrix(svm_prediction_tune_60,
                  test_set_60$target, positive = "1", mode = "prec_recall")
```


## Naive Bayes

### Oversampling
```{r  message=FALSE, eval = FALSE}

oversampledtraining60 <- ROSE::ovun.sample(target~., 
data = training_set_60, method = "over", p = 0.5, seed = 111)$data
```

### Tuning
```{r  message=FALSE, eval = FALSE}
search_grid <- expand.grid(
  usekernel = c(TRUE, FALSE),
  fL = 0:5,
  adjust = seq(0, 5, by = 1)
)
```

### Model
```{r  message=FALSE, eval = FALSE}
#install.packages("klaR")
library(klaR)

features <- setdiff(names(training_set_60), "target")
x <- training_set_60[, features]
y <- training_set_60$target

train_control <- trainControl(
method = "cv", 
number = 10
)

nb.m2 <- train(
  x = x,
  y = y,
  method = "nb",
  trControl = train_control,
  tuneGrid = search_grid,
  preProc = c("center", "scale", "pca")
  )

nb.m2$results %>% 
  top_n(5, wt = Accuracy) %>%
  arrange(desc(Accuracy))


pred <- predict(nb.m2, newdata = test_set_60)
(cf_nb_60 <- confusionMatrix(pred, test_set_60$target,
                  positive='1', mode = "prec_recall"))
```

## Neural Network

### SMOTE
```{r  message=FALSE, eval = FALSE}
#install.packages("DMwR")
library(DMwR)
smotedt <- as.data.frame(training_set_small)
smotedt$target <- as.factor(smotedt$target)

smote_round1 <-
  DMwR::SMOTE(
    form = target ~ .,
    data = smotedt,
    perc.over = 100,
    perc.under = 200
  )
```

### Model
```{r  message=FALSE, eval = FALSE}
#install.packages("neuralnet")
library(neuralnet)
nn=neuralnet(target~ ., data=smote_round1, hidden=100,act.fct = "logistic",
                linear.output = FALSE)

Predict=compute(nn,test_set_small)
prob <- Predict$net.result
pred <- ifelse(prob>0.5, "1", "0")
pred <- as.factor(pred[,2])
class(pred)

(cf_nn_70 <- confusionMatrix(pred, test_set_small$target, 
                     positive='1', mode = "prec_recall"))
```

\newpage

# Plots used in the report

## Exporting the outputs of the confusion matrices
```{r  message=FALSE, eval = FALSE}
tocsv <- data.frame()

#Named all variables with "cf_", so that we can easily 
#find all matrices and export them to csv
for (file in ls()){
  print(paste("testing file", file))
  if (stringr::str_detect(file, "cf_")){
    cm <- get(file)
    print(cm)
    tocsv2 <- data.frame(cbind(file, t(cm$overall),t(cm$byClass)))
    tocsv <- rbind(tocsv, tocsv2)
  }}


write.csv(tocsv,file="final_models.csv")
```

## Model comparsion plot
```{r message=FALSE, eval = FALSE}
library(ggplot2)
library(stringr)
library(gridExtra)
library(readxl)
library(tidyverse)

plotting_data <- read_excel("report_plot_models.xlsx")
plotting_data$Sample <- NULL
plotting_data$type <- as.factor(plotting_data$type)
plotting_data$Partition <- as.factor(plotting_data$Partition)
plotting_data$TP <- NULL

plotting_data_longer <- plotting_data %>% pivot_longer(5:8)

ggplot(plotting_data_longer) + geom_jitter(aes(x= type, y= value, color = Partition),
width = 0.1) + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
theme(legend.position = "bottom") + ylim(0, 1) + labs(x = NULL, y="Values") +
                                                            facet_grid(~name) 
```

## Expected profit model comparison chart
```{r message=FALSE, eval = FALSE}

cost_confusion_path <- "Cost Confusion Matrix.xlsx" 

cost_confusion_data <- read_excel(cost_confusion_path,sheet = "Plotting_Data")

cost_confusion_longer <- cost_confusion_data %>% pivot_longer(cols = c(Low_Cost,
High_Cost), names_to = "Cost_Type") %>% mutate(Cost_Type = factor(Cost_Type),
`Model_No_[]` = factor(`Model_No_[]`), Model_No = factor(Model_No)) 

levels(cost_confusion_longer$Cost_Type) <- c("High Cost Scenario", "Low Cost Scenario")

ggplot(cost_confusion_longer, aes(x= Model_No,y = value, fill = Cost_Type, 
color = factor(ifelse(Name=="RF 70% Stratified + Under 100 IG", "Yes", "No")))) + 
geom_col()+ facet_grid(~Cost_Type) + scale_fill_manual(values = c("#55e6b0", "#5cd5e0")) +
                            scale_color_manual( values=c("white", "black"), guide=FALSE) +
labs(y = "Expected Profit in £", fill = "Scenario",
x = "Model Number (see below for further information)") +
                      theme(legend.title=element_blank())
```

## Testing final model for overfitting plot
```{r message=FALSE, eval = FALSE}

plotting_data_final <- read.csv("final_models.csv")

plotting_data_final <- plotting_data_final %>% mutate(categorie = 
ifelse(str_detect(file, "train"), "Training", "Test"), type = "RF")

plotting_data_final_longer <- plotting_data_final %>% select("file", 
"Accuracy", "Precision", "Recall","F1" , "categorie","type") 

plotting_data_final_longer <- plotting_data_final_longer %>% 
pivot_longer(cols = c("Accuracy", "Precision", "Recall", "F1")) 

ggplot(plotting_data_final_longer) + geom_point(aes(x= name, y= value, 
color =categorie)) + ylim(0, 1) + 
labs(y = "Value in %", x = "Measure", col = "Set",
 title = "Testing final model on overfitting")

```

